%-------------------------------------------------------------------------------
%	Research Experience
%-------------------------------------------------------------------------------
\cvsection{Research Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Doctoral Researcher} % Job title
    {Computational Imaging Research Lab. (CIRL)} % Organisation
    {UoM, Memphis, TN} % Location
    {Aug. 2021-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{Working on the development of novel \textit{physics-guided image restoration} methods using \textit{Deep Learning (DL)} approaches to achieve super-resolution in 3D microscopy: Implemented physics-guided method using Super Resolution Network (SRN) and Residual Channel Attention GAN (caGAN) for microscopy image reconstruction.}
              \item{Collaborated with a four-person team (a collaboration between the University of Memphis and the University of Valencia) to publish new enhancements regarding the Tunable SIM design. My role was the Simulation of the Optical Transfer function (OTF) for WF, Tunable SIM, and 3Wave SIM Microscopes.}
              \item{Assisted a collaborator with data-acquisition code in \textit{LabView} from an open set-up Structured Illumination microscope under development. Then, improve the optical system implementation, imaging, and software.}
          \item {\textbf{Technical Skills:} Python with TensorFlow, NumPy, Matplotlib, Pandas, and Scikit-learn, MATLAB, \LaTeX, LabView, Optical Design, Git.}
        \item {\textbf{Soft Skills:} Teamwork, Problem Solving, Conflict resolution, Leadership, Adaptability, Presentation.}
      \end{cvitems}
    }
%---------------------------------------------------------
  
  \cventry
{Robotics R\&D Developer}  % Job title
    {\href{https://ir.linkedin.com/company/partdp-ai}{Part AI Research Center}} % Organisation
    {Tehran, Iran} % Location
    {Sep. 2020-Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
                \item{Robotics}
        \begin{itemize}[label= - ]
            \item {Designed, and built cooperative farming quad-copters from scratch}
             \item {Started learning and working with \textit{ROS}}
        \end{itemize}
        \item{Embedded Systems}
        \begin{itemize}[label=-]
            \item {Designed Flight Controller on Pixhauk Cube}
            \item {Developed the Raspberry Pi Linux on Erle Brain.}
            \item {Implemented Object Detection algorithms including \textit{YOLO} and YOLO LITE on embedded systems.}
            \item {Gave hardware embedded systems consultation.}
            \item {Started working with different embedded systems such as Khadas products and NVIDIA development boards.}
        \end{itemize}
        \item{Software}
        \begin{itemize}[label = -]
        \item {Design a software architecture, providing the class diagram for flight simulation APIs.}
            \item {Writing AI \textit{Python} APIs for Microsoft AirSim Flight Simulator.}
        \end{itemize}
        \item {\textbf{Technical Skills:} Sensor Fusion,, Python APIs, MATLAB, Git, Arduino, Embedded Systems, Docker, IOT, Robotics, Linux, Scrum, Kanban, etc.}
        \item {\textbf{Soft Skills:} Teamwork, Problem Solving, Conflict resolution, Leadership, Time Management, Adaptability.}
      \end{cvitems}
    } 
%---------------------------------------------------------

  \cventry
{Research Collaborator}  % Job title
    {University of New South Whales (UNSW)} % Organisation
    {Sydney, Australia} % Location
    {Aug. 2020-June 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Remote Collaboration in a team of four: Statistical data analysis on a genetics dataset: Applied different \textit{specificity tests} such as hypergeometric, chi-square, z-score, and fisher exact test, also using \textit{hierarchical clustering} to obtain tissue-specific genes, and consequently, disease causative genes.}
        \item {\textbf{Technical Skills:} Statistics, Matlab, and Python with NumPy, Matplotlib, Pandas, Scikit-learn.}
        \item {\textbf{Soft Skills:} Teamwork, Time management, Communication, Adaptability.}
      \end{cvitems}
    }
%---------------------------------------------------------
 
  \cventry
    {Research Collaborator}  % Job title
    {Institute for Brain and Cognitive Sciences} % Organisation
    {SBU, Tehran, Iran} % Location
    {Feb 2018-Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Developed a Human-Computer Interface for cyber-ball \& Iowa gambling task for checking patient rejection effect on risk-taking ability under supervision of Dr. Borhani.}
        \item {\textbf{Technical Skills:} Python GUI with pyqt and tKinter.}
        \item {\textbf{Soft Skills:} Problem Solving, Adaptability.}
      \end{cvitems}
    }
%---------------------------------------------------------
 
  \cventry
    {Undergraduate Research Assistant}  % Job title
    {Control of Multi-Vehicle Systems (CMVS) Laboratory} % Organisation
    {AUT, Tehran, Iran} % Location
    {Jan 2016-Aug 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
            \item{Thesis Project: The goal was to autonomously control a quadcopter and land it on a specific landing station using computer vision.}
          \item{Video processing with a camera connected to a \textit{Raspberry pi} in both \text{Python} and \textit{C++ } using \textit{OpenCV} and ARUCO markers.}
          \item{Designed separate PID controllers for each quadcopter's degrees of freedom.}
          \item{Connected \textit{C++ }code to \textit{Matlab} and control the UAV  on \textit{Matlab}, Simulink.}
          \item {Help to implement \textit{Fuzzy} systems and \textit{Neural Networks} in \textit{MATLAB} including modeling and control of a system, classification, regression and clustering, MLP trained with back-propagation, and machine learning.}
        \item {\textbf{Technical Skills:} C++, Python, OpenCV, Matlab, AI, Simulink, Embedded Systems, Sensor Fusion,IOT, Control System Design, Git.}
        \item {\textbf{Soft Skills:} Team Work, Leadership, Dependability, Problem Solving, Adaptability.}
      \end{cvitems}
    }   
%---------------------------------------------------------
 
  \cventry
 {Undergraduate Research Assistant}  % Job title
    {Parsian Robotics Center} % Organisation
    {AUT, Tehran, Iran} % Location
    {Jan 2013-Jan 2016} % Date(s)
    {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Small Size Soccer League:	Boost DC to DC converter design (Converting 16.8 v to 200 v),	Design a Two-way communication circuit using NRF module (wireless communication between robot and computer), Programming \textit{FPGA} using \textit{Verilog}, Full implementation of a microprocessor inside FPGA.}
            \item {Mirosot Soccer League:	Design the processor board (using FPGA) and the motor controller board}
            \item{Quadcopter: This project is considered an internship course. The goal was to convert a manually-controlled quadcopter into an autonomous robot. Design a board that contains the following: Processor, Motor drivers, IMU: gyroscope, magnetometer, and accelerometer, Two-way communication using NRF module, Vision using a distance sensor and an analog camera}
            \item {\textbf{Technical Skills:} Circuit Design, Microprocessors, FPGA, Sensor Fusion, Verilog, C++, IOT, Control System Design, Git.}
        \item {\textbf{Soft Skills:} Team Work, Dependability, Time Management, Adaptability.}
          \end{cvitems}
    }   
%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	Teaching Experience
%-------------------------------------------------------------------------------
\cvsection{Teaching Experience}


%-------------------------------------------------------------------------------
%	CONTENT:
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Mentor} % Job title
    {Virtually Integrated Program} % Organisation
    {UoM, Memphis, TN} % Location
    {August 2022 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mentoring undergraduate students with performing research, read and write papers, and learn programming languages including Python and Matlab.}
        \item {\textbf{Technical Skills:} Python, Matlab, Git.}
        \item {\textbf{Soft Skills:} Teamwork, Creativity, Dependability, Research.}
      \end{cvitems}
    }
%---------------------------------------------------------
  
  \cventry
    {Teacher Assistant}
    {Neuromatch Academy Online Summer School}
    {Online, USA}
    {July 2021 -  Aug. 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{\href{https://github.com/NeuromatchAcademy/course-content-dl}{Computational Neuroscience} \& \href{https://github.com/NeuromatchAcademy/course-content-dl}{Deep Learning}: Helping students to cooperate in hands-on coding and completing research projects}
        \item {\textbf{Technical Skills:} Python, NumPy, Scipy, Matplotlib, Git.}
        \item {\textbf{Soft Skills:} Teamwork, Problem Solving, Research, Communication.}
      \end{cvitems}
    }
%---------------------------------------------------------
 
  \cventry
    {Middle School Teacher}
    {NODET}
    {Tehran, Iran}
    {July 2013 -  May 2021}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Computer Programming}
          {Teach programming. Valuable projects has been completed and sent to different national and international competitions. Details are found \href{https://sites.google.com/view/steacher/farzanegan-1-high-school/junior-programming}{here}.}
        \item{Robotics Teacher}
          {Teach basics of analog and digital circuits. Teach to build different circuits and robots from scratch. Using C in CodeVision AVR to program robots. Students participated in different national competitions}
        \item {\textbf{Technical Skills:} Algorithm, Flowchart, Graph Theory, QT, C, C++, Python, Small Basic, Scratch, Circuit Design, Micro-controllers.}
        \item {\textbf{Soft Skills:} Research, Problem Solving, Creativity.}
      \end{cvitems}
    }
%---------------------------------------------------------

\cventry
{Workshop Instructor}
{Science Student Council}
{Tehran, Iran}
{July - Aug. 2020}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{MATLAB workshop at Science Students Council, Electrical Engineering Dept. Teach fundamentals of MATLAB and Simulink.}
  \end{cvitems}
}
%---------------------------------------------------------

\cventry
{Workshop Instructor}
{Sharif University of Technology}
{Tehran, Iran}
{June 2020}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Python workshop at Sharif Business Summer School. Teach Python basics to Object-Oriented Programming.}
  \end{cvitems}
}
%---------------------------------------------------------

\cventry
{Workshop Instructor}
{Science Student Council}
{AUT, Tehran, Iran}
{Jan. 2018-Aug. 2019}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{FPGA workshop Instructor at Science Students Council, Electrical Engineering Dept. Teaching FPGA from basic to full implementation (Verilog).}
  \end{cvitems}
}
%---------------------------------------------------------

\cventry
{Lab. Instructor \& Teaching Assistant}
{Computational Intelligence Program}
{AUT, Tehran, Iran}
{Jan. 2018-Aug. 2019}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Help to solve \textit{MATLAB} problems of online and offline learning using \textit{Neural Networks} and \textit{Fuzzy} Logic. Grade assignments, project presentation and reports.}
    \item{Adjust the lesson plan for the Computational Intelligence lab. course.}
    \item{Work on the full control system and modeling of a UGV using computational intelligence and full implementation of the lesson plan on the vehicle.}
    \item {\textbf{Technical Skills:} MATLAB, Simulink, Neural Networks, Fuzzy Logic, Controller Design.}
\item {\textbf{Soft Skills:} Problem Solving.}
  \end{cvitems}
}
%---------------------------------------------------------

\cventry
{Mentor}
{Quera.ir}
{Online, Iran}
{June-Aug 2020}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Help high school students from to learn C++, solve problems, cooperate in teams, and complete a project.}
  \end{cvitems}
}
%---------------------------------------------------------

\cventry
{Tutor}
{Freelance}
{Iran}
{2011-Aug. 2020}
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item{Topics: Robotics, Python, Matlab, C++, Machine Learning, ICDL, algorithm and flowchart, etc..}
  \end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
